---
title: "Homework4"
author: "Swetha Jayapathy"
date: "10/27/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
```{r imp}
library(Sleuth3)
library(ggplot2)
```

Question 1a
```{r Instate, echo= FALSE}
qplot(Type, InState, data=ex0332, geom="boxplot")
```
Question 1b
The plot shows that the equal variance assumption is violated as we can see that the InState tuition fees for Private colleges have a bigger spread(box is taller) compared to the InState Public colleges.

Question 1c

µ1 - Mean InState tuition at private universities 
µ2 - Mean InState tuition at public universities. 

Null Hypothesis (H0):
µ1 -  µ2 = 0
There is no difference in the mean InState tuition fees for the Private Universities and that of Public Universities.

Alternate Hypothesis (HA):
µ1 -  µ2 > 0
The mean InState tuition fees for the Private colleges is higher than that of Public colleges.

Question 1d

```{r welch test}
t.test(InState~Type,data=ex0332,alternative="greater")
```

Question 1e
Statistical Conclusion
There is a significant evidence that the mean InState tuition fees is higher for Private Universities than the Public Universities with a one sided Welch's test p value < 0.0001


Question 1f
Statistical Conclusion
We estimate increase in mean InState tuition fees between Private Universities and Public Universities in the range $13951.51 and $28563.45 with 95% Confidence level.

Question 2a

Consider the following:
Y = Survival time of random participant in Control group.
Y + δ = Survival time of same participant in therapy group.
Where δ is the shift parameter which represents the difference between the two groups.

Null Hypothesis:
The Shift parameter(δ) is zero, there is no effect of therapy on the life expectancy.

Alternate Hypothesis:
The Shift parameter(δ) is non-Zero, there is an effect of therapy on the life expectancy.

Question 2b
```{r tt}
wilcox.test(Survival~Group, data=ex0431, exact=FALSE, correct=FALSE,conf.int=TRUE, alternative="less")
```

Question 2c
There is no evidence that the survival time of breast cancer patients on therapy is higher than those without the therapy which is indicated by the p-value of 0.1308 (one-sided Wilcoxon rank sum test).

Question 3
```{r Signtest}
HW2Dat <- read.csv("D:/D drive contents/Fall 2020/Stats 511/Class/HW/HW2/NavDat.csv")
diffs <- with(HW2Dat, DT-M)
l <- length(diffs)
g <- length(which(diffs>0))
```

```{r 3}
binom.test(g, l, alternative="two.sided")
```
