---
title: "Homework 6"
author: "Swetha Jayapathy"
date: "11/17/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r imp}
library(Sleuth3)
library(ggplot2)
```

Question 1:

a) df for Treatment= 4
```{r 1a}
68-64
```
b) Sum of Squares for Treatment = 1226.9
```{r 1b}
5953.5 - 4726.6 
```
c) Mean Squares of Treatment = 306.725
```{r 1c}
1226.9/4
```
d) F-Stat = 4.153183
```{r 1d}
306.725/73.853
```

e) Residual Mean Square:  = 73.853
```{r 1e}
4726.6/64
```


Question 2a:
Response variable is Oxygen.
```{r 2a}
head(ex0523)
```
Question 2b:

```{r 2b}
ex0523_aov <- aov(Oxygen~Bone, data = ex0523)
anova(ex0523_aov)
```

Question 2c:

Let µ{Yij} be the population mean of population where we got Yij.

Full model:
Full model is also known as Separate means model.
                  µ{Yij} = µi 
Where µi is the ith population mean and there are 'I' mean parameters.That is each group has its own mean :µ1, µ2......µi.In the Full model, Yij is normally distributed with standard deviation sigma.

Reduced model:
Reduced model is also known as Equal means model
                  µ{Yij} = µ 
where µ is the only mean parameter.The population here is normally distributed with standard deviation sigma.This is a special case of Separate means model.


Question 2d:
Extra sum of squares = 6.0675
Extra degrees of freedom = 11
Residual sum of squares for the full model = 2.9708
Residual degrees of freedom for the full model = 40 


Question 2e:
```{r 2e}
fitex0523_aov <- aov(Oxygen~1, data=ex0523)
anova(fitex0523_aov)
```

Question 2f:
Residual sum of squares for the reduced model in part (c) = 9.0383
Residual degrees of freedom for the reduced model in part (c) = 51


Question 2g:
Residual sum of squares for the reduced model =  9.0383
Residual sum of squares for the Full model = 2.9708
```{r 2g}
9.0383-2.9708
```
Therefore, the answer is equal to the extra sum of squares in part(d).


Question 2h:
Number of mean parameters in full model = 12
Number of mean parameters in reduced model = 1

Confirming that the extra degrees of
freedom in part (d) is equal to the difference in number of mean parameters between
the full and reduced models :
```{r 2ha}
12-1
```

Confirming that this difference is same as the
difference between the residual degrees of freedom for the reduced model(51) and the
residual degrees of freedom for the full model(40).
```{r 2hb}
51-40
```