---
title: "HW8_Jayapats"
author: "Swetha Jayapathy"
date: "12/2/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r imp}
library(Sleuth3)
library(ggplot2)
```


```{r h}
head(ex0728)
```

Question 1
Produce a scatterplot of Activity vs. Years with fitted regression line. Include R code and the plot. Does the linearity assumption appear to be met?


Yes, from the below plot we can say that the linearity assumption is met.

```{r 1, echo=TRUE}
ggplot(ex0728, aes(x=Years, y=Activity))+
geom_point(size=I(4))+
geom_smooth(method = lm, se=FALSE)
```


Question 2

```{r Q2, , results="hide"}
ex0728_lm <- lm(Activity~Years, data=ex0728)
summary(ex0728_lm)
```

```{r Q2b, , results="hide"}
ex0728_lm$coefficients
```

Estimated Regression equation:
µ{Xi|Yi} = 8.3873 + 0.9971(Xi)


                                        (1.1149)   (0.1110)

Xi = Years,

Yi = Activity



Question 3
```{r Q3, , results="hide"}
confint(ex0728_lm)
```

Confidence Interval for Intercept =5.9786877 to 10.79582


Confidence Interval for Slope prameters = 0.7572415 to 1.23704



Question 4

Statistical Conclusion:
We estimate the population mean neuronal activity index after 0 years of playing string instrument is 5.9786877 to 10.79582 units (95% CI, SLR).




Question 5
```{r Q5}
predict(ex0728_lm, data.frame(Years= 15), se.fit = TRUE,interval = "confidence")
```
Statistical Conclusion:
We estimate the population mean neuronal activity index after 15 years of playing a string instrument is 20.83057 to 25.85816 units (95% CI, SLR).



Question 6
```{r Q6}
predict(ex0728_lm, data.frame(Years= 15), se.fit = TRUE,interval = "prediction")
```
Statistical Conclusion:
It is predicted that the neuronal index after 15 years of playing a string instrument is 16.37407 to 30.31466 units (95% PI, SLR).
