---
title: "Homework2"
author: "Swetha Jayapathy"
date: "10/13/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


```{r imp}
library(Sleuth3)
library(ggplot2)
```

```{r importData}
HW2Dat <- read.csv("D:/D drive contents/Fall 2020/Stats 511/Class/HW/HW2/NavDat.csv")
```

```{r Data}
head(HW2Dat)
```


Question 1a :
```{r CalcDiffs}
diffs <- with(HW2Dat, DT-M)
diffs
```


Question 1b :
qplot(diffs, geom="histogram")

```{r diffs, echo= TRUE}
qplot(diffs, geom="histogram")
```
Question 1c
```{r 1ca}
(Ybar <- mean(diffs)) #Calculate the sample mean of the differences
```

```{r 1cb}
(s <- sd(diffs))     #Calculate the sample standard deviation
```
```{r 1cc}
(n <- length(diffs))         #Find the sample size
```

Question 1d
```{r SE}
(se_Ybar <- s/sqrt(n))    #Calculate the SE of the sample mean
```       
```{r tstat}
Ybar/se_Ybar #t-statistics
```       

Question 1e
```{r tstatFormula}
with(HW2Dat, t.test(DT, M, paired=TRUE))
```       

Question 2a

```{r HumerusHist, echo= FALSE}
qplot(Status, Humerus, data=ex0221, geom="boxplot")
```
Statistical Conclusion:

According to the 2 sample t-test, we can say that there is no significant evidence against the null hypothesis ; that is the mean difference of the length of humerus between the perished and the survived is non-zero (p-value = 0.0809). The mean differences between that of perished and survived from the t-test is 0.01 with a 95% confidence interval in the range -0.021446053 to 0.001279386.




Question 2b
```{r ttest}
# To get 2 sided Confidence Interval
t.test(Humerus~Status, data=ex0221, var.equal=TRUE)
```      


```{r Humerus, echo= TRUE}
qplot(Status, Humerus, data=ex0221, geom="boxplot")
```


Question 3
(a) Describe what is meant by the sampling distribution of the sample standard deviation.

Sampling distribution of the sample standard deviation is the distribution under repeated sampling of the standard deviation which is computed by taking particular sample size of n samples from a population. This is the distribution which we get when we take an arbitrary number of samples and calculate the standard deviation of all the samples to plot in graph.


(b) Describe what is meant by the sampling distribution of the sample maximum.

Sampling distribution of the sample maximum is the distribution under repeated sampling of the maximum value which is computed by taking particular sample size of n samples from a population. This requires us to compute the sample maximum for each of the n samples. The distribution of these n sample maximum is the sampling distribution of sample standard deviations.








